---
title: "Simulating Barcoded Sequencing Data with BarcoSim"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{BarcoSim-vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
library(BarcoSim)
```

<h1>Introduction</h1>

<p>Barcoded sequencing is a technique used in genomics research to simultaneously sequence many samples while identifying the sample origin of each sequence. The BarcoSim R package provides tools to simulate barcoded sequencing data for testing analysis methods.</p>

<p>Key features:</p>

<ul>
<li>Generate parent DNA sequences with specified barcode regions</li>  
<li>Analyze similarity across barcode regions</li>
<li>Replicate sequences with errors to mimic sequencing</li>
<li>Analyze and process the simulated data</li>
</ul>

<h1>Generating Parent Sequences</h1>

<p>The `gpseq()` function creates the initial parent DNA sequences with defined barcode regions:</p>

```{r gpseq, echo=TRUE}
library(BarcoSim) 

# 5 sequences of length 10 with barcodes from 3-6
seqs <- gpseq(5, 10, 3, 6)  

print(seqs)
```

<p>Multiple discontinuous barcode regions can be specified using vectors for `range_start` and `range_end`.</p> <h1>Analyzing Similarity</h1> <p>`calcSeqSim()` computes the percentage similarity at each position:</p>
